%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{bookmark}
\usepackage{fancyhdr}
\setlength{\footskip}{12pt}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep, topsep=0pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  {\Huge\textsc{Avinash Nandyala}} \\ \vspace{1pt}
  \small +1 (413) 466-4833 $|$ \href{mailto:anandyala@umass.edu}{\underline{anandyala@umass.edu}} $|$
  \href{https://www.linkedin.com/in/avinash-nandyala-06a88b199/}{\underline{LinkedIn}} $|$
  \href{https://github.com/navinash47}{\underline{Github}} $|$
  \href{https://navinash47.github.io/Portfolio/}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\begin{center}
  \small{MS CS candidate at UMass Amherst with 3 years of software engineering experience at Mastercard building secure REST APIs, microservices, and distributed backend systems. Active research in reinforcement learning, LLM fine-tuning with RLHF, and continual learning. Skilled at building and deploying AI-powered backend services using PyTorch, HuggingFace, Spring Boot, and Python.}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Massachusetts Amherst}{Amherst, MA}
    {Master of Science in Computer Science}{Expected May 2026}
  \resumeSubheading
    {Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}
    {Bachelor of Technology in Computer Science and Engineering}{May 2021}
\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, Java, C, C++, C\#, JavaScript, SQL} \\
    \textbf{Frameworks / Libraries}{: PyTorch, TensorFlow, HuggingFace, Scikit-learn, Spring Boot, .NET Core, ASP.NET, JUnit, NumPy, Pandas, CUDA} \\
    \textbf{Tools / Platforms}{: ROS, Isaac Gym, Genesis, MuJoCo, Linux, Jenkins, Docker, Google Cloud Platform (GCP), Oracle SQL, Git, Jupyter, Weights \& Biases (W\&B), IntelliJ, Visual Studio, Android Studio} \\
    \textbf{Certifications}{: DeepLearning.AI: ML Specialization, DL Specialization, NLP Specialization}
  }}
\end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Graduate Research Assistant, Human-Centric Robotics Lab}{May 2025 -- Present}
    {University of Massachusetts Amherst}{Amherst, MA}
    \resumeItemListStart
      \resumeItem{Developing a continual learning framework for quadruped locomotion using Kolmogorov--Arnold Networks (KANs) with B-spline edge representations, enabling localized task updates that prevent global interference in MLP policies.}
      \resumeItem{Implemented BeamDojo extensions for humanoid locomotion, developing reinforcement learning algorithms for balance and control on sparse footholds.}
      \resumeItem{Ported the Visual Whole-Body Control framework from Isaac Gym to Genesis, unlocking advanced loco-manipulation and physics-based motion planning in a more efficient differentiable simulation environment.}
    \resumeItemListEnd

  \resumeSubheading
    {Graduate Research Assistant, Biomedical NLP Lab}{Feb. 2025 -- May 2025}
    {University of Massachusetts Amherst}{Amherst, MA}
    \resumeItemListStart
      \resumeItem{Fine-tuned large language models (Qwen, LLaMA) using DeepSeek-RL and reinforcement learning with human feedback (RLHF) for biomedical text understanding, achieving 85\% accuracy on clinical datasets.}
      \resumeItem{Benchmarked model performance across MIMIC-EXT-IV and RARE datasets to evaluate robustness and domain generalization in biomedical NLP.}
      \resumeItem{Enhanced model interpretability and domain-specific reasoning through reinforcement alignment and reward optimization techniques.}
    \resumeItemListEnd

  % \resumeSubheading
  %   {Graduate Research Assistant}{Feb. 2025 -- Present}
  %   {University of Massachusetts Amherst}{Amherst, MA}
  %   \resumeItemListStart
  %     \resumeItem{Developing a continual learning framework for quadruped locomotion using Kolmogorov--Arnold Networks (KANs) with B-spline edge representations, enabling localized task updates that prevent global interference in MLP policies.}
  %     \resumeItem{Implemented BeamDojo extensions for humanoid locomotion, developing reinforcement learning algorithms for balance and control on sparse footholds.}
  %     \resumeItem{Ported the Visual Whole-Body Control framework from Isaac Gym to Genesis, unlocking advanced loco-manipulation and physics-based motion planning in a more efficient differentiable simulation environment.}
  %     \resumeItem{Fine-tuned large language models (Qwen, LLaMA) using DeepSeek-RL and RLHF for biomedical text understanding, achieving 85\% accuracy on clinical datasets; benchmarked across MIMIC-EXT-IV and RARE datasets for domain generalization.}
  %     \resumeItem{Enhanced model interpretability and domain-specific reasoning through reinforcement alignment and reward optimization techniques.}
  %   \resumeItemListEnd

  \resumeSubheading
    {Software Engineer}{Jul. 2021 -- Jul. 2024}
    {Mastercard}{Pune, India}
    \resumeItemListStart
      \resumeItem{Contributed to the Enhanced Currency Conversion (ECC) system by developing secure REST APIs and ASP.NET web services to streamline international transaction processing.}
      \resumeItem{Engineered compliance-ready features for PCI key block mandates (CAVV, HMAC), strengthening cryptographic integrity and data protection.}
      \resumeItem{Led modernization of gateway services from Java 8 to Zulu 17, resolving build pipeline issues on Jenkins and mitigating production vulnerabilities in tokenization microservices.}
      \resumeItem{Mentored interns on automated environmental stability reports for Mastercard Local Processing Services, reducing manual monitoring overhead by 25\% through automated alerting and report generation.}
      \resumeItem{Enhanced the FLD (Fraud and Loss Disputes) platform by improving dispute resolution workflows in a microservices-based backend system, achieving 100\% test pass rate through rigorous testing, debugging, and validation.}
    \resumeItemListEnd

  \resumeSubheading
    {Undergraduate Research Assistant, NLP Lab}{Mar. 2021 -- Jun. 2021}
    {IIT Kharagpur}{Kharagpur, India}
    \resumeItemListStart
      \resumeItem{Developed legal judgment classification systems using BiLSTM-BERT hybrid models, automating case categorization from Indian and UK Supreme Court datasets.}
      \resumeItem{Improved legal text comprehension accuracy with domain-adaptive fine-tuning, achieving F1-scores of 0.69 (India) and 0.55 (UK), surpassing vanilla BERT fine-tuning baselines on both datasets.}
    \resumeItemListEnd

  \resumeSubheading
    {Undergraduate Research Assistant, SWAN Laboratory}{Jun. 2020 -- Jan. 2021}
    {IIT Kharagpur}{Kharagpur, India}
    \resumeItemListStart
      \resumeItem{Designed an IoT-enabled healthcare prediction system integrating dense neural networks to compute patient criticality scores, supporting urgency-aware clinical triage decisions.}
      \resumeItem{Built a hospital recommender engine using KNN and cosine similarity, deployed on Google Cloud, providing real-time facility recommendations within a 5km radius.}
    \resumeItemListEnd

  \resumeSubheading
    {Software Engineer Intern}{May 2020 -- Jun. 2020}
    {Mastercard}{Pune, India}
    \resumeItemListStart
      \resumeItem{Designed and simulated an end-to-end point-of-sale (POS) system for contactless card transactions using C and Arduino Wi-Fi modules, validating the full transaction flow from card tap to approval.}
      \resumeItem{Documented hardware-software integration findings and presented prototype results to the engineering team, informing the go/no-go decision for the contactless payment prototype rollout.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

%   \resumeProjectHeading
%     {\textbf{BioNLP Model Alignment using DeepSeek-RL} $|$ \emph{PyTorch, LLMs, RLHF, HuggingFace}}{}
%     \resumeItemListStart
%       \resumeItem{Aligned large language models (Qwen, LLaMA) using DeepSeek-RL for biomedical NLP tasks, achieving 85\% accuracy with RLHF versus 60\% with supervised fine-tuning on clinical datasets.}
%       \resumeItem{Benchmarked domain generalization across MIMIC-EXT-IV and RARE datasets, evaluating robustness through reinforcement alignment and reward optimization.}
%     \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Fault-Tolerant Quadrupedal Locomotion with Flow Matching} $|$ \emph{PyTorch, RL, Robotics}}{}
    \resumeItemListStart
      \resumeItem{Integrated fault-tolerant control mechanisms with flow-matching algorithms for robust quadrupedal locomotion under actuator and sensor failures.}
      \resumeItem{Built on DreamFLEX's fault-aware locomotion controller and DreamWaQ's terrain imagination capabilities to maintain smooth, adaptive movement across diverse terrains.}
      \resumeItem{Optimized trajectory generation for enhanced stability and energy efficiency using differentiable simulation and policy optimization.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Adaptive Personalized Travel Information Simulation} $|$ \emph{Python, Probabilistic Inference}}{}
    \resumeItemListStart
      \resumeItem{Developed a simulation system for real-time analysis of traveler choices and adaptation behavior, using the Metropolis-Hastings algorithm and efficient approximations to reduce computation time from 382s to 1.79s over an existing Gibbs sampling approach.}
    \resumeItemListEnd

%   \resumeProjectHeading
%     {\textbf{Data Conversion to YouTube Video for Unlimited Storage} $|$ \emph{Python, YouTube Data API}}{}
%     \resumeItemListStart
%       \resumeItem{Developed a web application that encodes arbitrary binary data into video frames and uploads it to YouTube via the YouTube Data API, enabling an unconventional approach to scalable cloud storage.}
%       \resumeItem{Designed a full pipeline covering binary-to-pixel encoding, video generation, API-authenticated upload, and retrieval decoding, demonstrating end-to-end systems thinking.}
%     \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Bus Management System} $|$ \emph{Java, Spring Boot, REST APIs, Oracle SQL, Docker}}{}
    \resumeItemListStart
      \resumeItem{Built a full-stack bus fleet management system using Spring Boot and REST APIs, supporting real-time route tracking, schedule management, and driver assignment for 200+ bus routes.}
      \resumeItem{Designed an Oracle SQL schema for fleet data and integrated Docker-based deployment, reducing environment setup time and enabling consistent CI/CD pipelines.}
    \resumeItemListEnd

%   \resumeProjectHeading
%     {\textbf{Hierarchical Context Aggregation for Medical Notes} $|$ \emph{Python, NLP}}{}
%     \resumeItemListStart
%       \resumeItem{Implemented spoken language normalization achieving 90\% accuracy in medical terminology grounding.}
%       \resumeItem{Developed key-phrase extraction and topic categorization algorithms for SOAP note generation.}
%     \resumeItemListEnd

%   \resumeProjectHeading
%     {\textbf{SemEval 2021 Task 8 – MeasEval} $|$ \emph{PyTorch, RoBERTa, NLP}}{}
%     \resumeItemListStart
%       \resumeItem{Participated in SemEval 2021 Task 8 (MeasEval Counts and Measurement) focusing on semantic extraction between measured entities and measured quantities.}
%       \resumeItem{Used RoBERTa-large and CRF models in PyTorch to reach an F1-score of 0.54.}
%     \resumeItemListEnd

%   \resumeProjectHeading
%     {\textbf{Patrol Bot – Autonomous Security Robot} $|$ \emph{ROS, OpenCV, C++}}{}
%     \resumeItemListStart
%       \resumeItem{Developed an autonomous patrol robot integrating OpenCV-based vision for person detection and obstacle avoidance.}
%       \resumeItem{Implemented a color-coded feedback system and conducted real-world testing in indoor environments.}
%     \resumeItemListEnd

%   \resumeProjectHeading
%     {\textbf{Advanced Robot Navigation and Localization} $|$ \emph{Python, Robotics}}{}
%     \resumeItemListStart
%       \resumeItem{Developed a particle filter algorithm for robot localization achieving 0.5m position accuracy.}
%       \resumeItem{Implemented and compared Q-learning and SARSA algorithms for autonomous robot wall-following with 100\% success rate in complex scenarios.}
%     \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------HONORS & AWARDS-----------
\section{Honors \& Awards}
\resumeSubHeadingListStart
  \resumeItem{\textbf{IIT Kharagpur -- JEE Advanced} (2017): Admitted through one of India's most competitive engineering examinations, with acceptance among the top 0.1\% of over 1.2 million applicants nationwide.}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}