%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{bookmark}
\usepackage{fancyhdr}
\setlength{\footskip}{12pt}
% \usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep, topsep=0pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
  {\Huge\textsc{Avinash Nandyala}} \\ \vspace{1pt}
  \small +1 (413) 466-4833 $|$ \href{mailto:anandyala@umass.edu}{\underline{anandyala@umass.edu}} $|$
  \href{https://www.linkedin.com/in/avinash-nandyala-06a88b199/}{\underline{LinkedIn}} $|$
  \href{https://github.com/navinash47}{\underline{Github}} $|$
  \href{https://navinash47.github.io/Portfolio/}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\begin{center}
  \small{MS CS candidate at UMass Amherst with active research in robot learning, locomotion control, and NLP. Experienced in reinforcement learning for quadruped and humanoid systems, fine-tuning LLMs with RLHF, physics-based simulation (Isaac Gym, Genesis, MuJoCo), and building production-grade Java enterprise systems. 3 years of industry experience at Mastercard developing secure REST APIs, microservices, and distributed backend systems. Strong foundation in system design, DBMS, cryptographic compliance, and scalable application development.}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Massachusetts Amherst}{Amherst, MA}
    {Master of Science in Computer Science}{Expected May 2026}
  \resumeSubheading
    {Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}
    {Bachelor of Technology in Computer Science and Engineering}{May 2021}
\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, Java, C, C++, C\#, JavaScript, SQL} \\
    \textbf{Frameworks / Libraries}{: PyTorch, TensorFlow, HuggingFace, Scikit-learn, NumPy, Pandas, OpenCV, CUDA, Spring Boot, .NET Core, ASP.NET, Hibernate, JUnit, Mockito, Maven, Gradle, Next.js} \\
    \textbf{Tools / Platforms}{: ROS, Isaac Gym, Isaac Sim, Genesis, MuJoCo, Linux, Docker, Jenkins, Git, Jupyter, Weights \& Biases (W\&B), Google Cloud Platform (GCP), Oracle SQL, Postman, IntelliJ, Visual Studio, Android Studio, REST APIs, Microservices} \\
    \textbf{Certifications}{: DeepLearning.AI: ML Specialization, DL Specialization, NLP Specialization}
  }}
\end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Graduate Research Assistant, Human-Centered Robotics Lab}{May 2025 -- Present}
    {University of Massachusetts Amherst}{Amherst, MA}
    \resumeItemListStart
      \resumeItem{Developing a continual learning framework for quadruped locomotion using Kolmogorov--Arnold Networks (KANs) with B-spline edge representations, enabling localized task updates that prevent global interference in MLP policies.}
      \resumeItem{Implemented BeamDojo extensions for humanoid locomotion and developed reinforcement learning algorithms in ROS that improve balance and control on sparse footholds, resulting in more stable gait execution.}
      \resumeItem{Ported the Visual Whole-Body Control framework from Isaac Gym to Genesis, enabling advanced loco-manipulation and physics-based motion planning in a more efficient differentiable simulation environment.}
      \resumeItem{Investigated collision-reach tradeoffs in quadruped loco-manipulation using a Unitree B1 + Z1 arm in Isaac Lab; swept six collision penalty weight configurations (w $\in$ [0.1, 1.0]) with PPO, identifying an optimal range w $\in$ [0.25, 0.35] that improved end-effector tracking by 18\% and expanded reachable workspace by 23\% while maintaining a 97\% locomotion success rate.}
    \resumeItemListEnd

  \resumeSubheading
    {Graduate Research Assistant, Biomedical NLP Lab}{Feb. 2025 -- May 2025}
    {University of Massachusetts Amherst}{Amherst, MA}
    \resumeItemListStart
      \resumeItem{Fine-tuned large language models (Qwen, LLaMA) using DeepSeek-RL and reinforcement learning with human feedback (RLHF) for biomedical text understanding, achieving 85\% accuracy on clinical datasets.}
      \resumeItem{Benchmarked model performance on the MIMIC-EXT-IV and RARE biomedical datasets using Scikit-learn, revealing improved robustness and better domain generalization across clinical text.}
      \resumeItem{Enhanced model interpretability and domain-specific reasoning through reinforcement alignment and reward optimization techniques.}
    \resumeItemListEnd

  \resumeSubheading
    {Software Engineer}{Jul. 2021 -- Jul. 2024}
    {Mastercard}{Pune, India}
    \resumeItemListStart
      \resumeItem{Developed secure REST APIs and ASP.NET web services for the Enhanced Currency Conversion (ECC) system using C\# and .NET, improving processing efficiency and reducing latency for international transactions.}
      \resumeItem{Engineered compliance-ready features for PCI key block mandates (CAVV, HMAC), strengthening cryptographic integrity and data protection.}
      \resumeItem{Led modernization of gateway services from Java 8 to Zulu 17, resolving build pipeline issues on Jenkins and mitigating production vulnerabilities in tokenization microservices.}
      \resumeItem{Mentored interns on automated environmental stability reports for Mastercard Local Processing Services, reducing manual monitoring overhead by 25\% through automated alerting and report generation.}
      \resumeItem{Enhanced the FLD (Fraud and Loss Disputes) platform by improving dispute resolution workflows in a microservices-based backend system, achieving 100\% test pass rate through rigorous testing, debugging, and validation.}
    \resumeItemListEnd

  \resumeSubheading
    {Undergraduate Research Assistant, NLP Lab}{Mar. 2021 -- Jun. 2021}
    {IIT Kharagpur}{Kharagpur, India}
    \resumeItemListStart
      \resumeItem{Developed legal judgment classification system with BiLSTM-BERT hybrid models using TensorFlow and HuggingFace, automating case categorization for Indian and UK Supreme Court datasets and reducing manual sorting effort.}
      \resumeItem{Improved legal text comprehension accuracy with domain-adaptive fine-tuning, achieving F1-scores of 0.69 (India) and 0.55 (UK), surpassing vanilla BERT fine-tuning baselines on both datasets.}
    \resumeItemListEnd

  \resumeSubheading
    {Undergraduate Research Assistant, SWAN Laboratory}{Jun. 2020 -- Jan. 2021}
    {IIT Kharagpur}{Kharagpur, India}
    \resumeItemListStart
      \resumeItem{Designed an IoT-enabled healthcare prediction system integrating dense neural networks to compute patient criticality scores, improving emergency triage accuracy by 40\%.}
      \resumeItem{Built a hospital recommender engine using KNN and cosine similarity, deployed on Google Cloud, providing real-time facility recommendations within a 5km radius.}
      \resumeItem{Automated real-time hospital data updates via Google Maps API and web scraping, ensuring hourly synchronization and high data reliability.}
    \resumeItemListEnd

  \resumeSubheading
    {Software Engineer Intern}{May 2020 -- Jun. 2020}
    {Mastercard}{Pune, India}
    \resumeItemListStart
      \resumeItem{Designed and simulated an end-to-end point-of-sale (POS) system for contactless card transactions using C and Arduino Wi-Fi modules, validating the full transaction flow from card tap to approval.}
      \resumeItem{Documented hardware-software integration findings and presented prototype results to the engineering team, contributing to product feasibility evaluation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

%  \resumeProjectHeading
%    {\textbf{Fault-Tolerant Quadrupedal Locomotion with Flow Matching} $|$ \emph{PyTorch, RL, Robotics}}{}
%    \resumeItemListStart
%      \resumeItem{Integrated fault-tolerant control mechanisms with flow-matching algorithms for robust quadrupedal locomotion under actuator and sensor failures.}
%      \resumeItem{Built on DreamFLEX's fault-aware locomotion controller and DreamWaQ's terrain imagination capabilities to maintain smooth, adaptive movement across diverse terrains.}
%      \resumeItem{Optimized trajectory generation for enhanced stability and energy efficiency using differentiable simulation and policy optimization.}
%    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Hierarchical Context Aggregation for Automated Medical SOAP Notes}}{Mar. 2025 -- May 2025}
    \resumeItemListStart
      \resumeItem{Designed and implemented a modular pipeline (Approach 3) combining LLM-prompted key phrase extraction via Qwen 3, BiomedBERT prompt-aware embeddings, and agglomerative hierarchical clustering with k-means subclustering to structure doctor-patient transcripts into SOAP-format clinical notes.}
      \resumeItem{Built a multi-strategy SOAP section classifier using an ensemble of embedding cosine similarity, LDA topic modeling with Hungarian assignment, and zero-shot NLI (BART-MNLI), achieving majority-vote label assignment across subclusters.}
      \resumeItem{Achieved the lowest GPT-2 perplexity (21.35 vs. 26.51 baseline, 51.28 fine-tuned) and highest BioBERT embedding similarity (0.3148 vs. 0.4446 baseline) among all approaches, indicating superior fluency and medical terminology alignment.}
      \resumeItem{Implemented text normalization with regex-based filler removal, measurement standardization, and sentence recapitalization across 207 ACI-Bench transcripts.}
      \resumeItem{Evaluated across 6 metrics including QA-based factual consistency (T5 + DistilBERT), BERTScore F1 with SciBERT, and LLM-as-a-Judge scoring via DeepSeek-R1 across Subjective, Objective, Assessment, and Plan sections.}
      \resumeItem{\textbf{Tech}{: Python, Qwen 3, BiomedBERT, BART-MNLI, scikit-learn, HuggingFace Transformers, Ward's linkage clustering}}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Visual Whole-Body Control: Isaac Gym to Genesis Port} $|$ \emph{PyTorch, Isaac Gym, Genesis}}{}
    \resumeItemListStart
      \resumeItem{Ported the Visual Whole-Body loco-manipulation framework from Isaac Gym to the Genesis simulation environment, enabling advanced whole-body control in a more efficient differentiable simulator.}
      \resumeItem{Implemented configuration management and optimized robotic locomotion and manipulation policies using PyTorch and JIT compilation for improved training throughput.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{BioNLP Model Alignment using DeepSeek-RL} $|$ \emph{PyTorch, LLMs, RLHF, HuggingFace}}{}
    \resumeItemListStart
      \resumeItem{Aligned large language models (Qwen, LLaMA) using DeepSeek-RL for biomedical NLP tasks, achieving 85\% accuracy with RLHF versus 60\% with supervised fine-tuning on clinical datasets.}
      \resumeItem{Benchmarked domain generalization across MIMIC-EXT-IV and RARE datasets, evaluating robustness through reinforcement alignment and reward optimization.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Hierarchical Context Aggregation for Medical Notes} $|$ \emph{Python, NLP}}{}
    \resumeItemListStart
      \resumeItem{Implemented spoken language normalization achieving 90\% accuracy in medical terminology grounding.}
      \resumeItem{Developed key-phrase extraction and topic categorization algorithms for SOAP note generation.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{SemEval 2021 Task 8 – MeasEval} $|$ \emph{PyTorch, RoBERTa, NLP}}{}
    \resumeItemListStart
      \resumeItem{Participated in SemEval 2021 Task 8 (MeasEval Counts and Measurement) focusing on semantic extraction between measured entities and measured quantities.}
      \resumeItem{Used RoBERTa-large and CRF models in PyTorch to reach an F1-score of 0.54.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Patrol Bot – Autonomous Security Robot} $|$ \emph{ROS, OpenCV, C++}}{}
    \resumeItemListStart
      \resumeItem{Developed an autonomous patrol robot integrating OpenCV-based vision for person detection and obstacle avoidance.}
      \resumeItem{Implemented a color-coded feedback system and conducted real-world testing in indoor environments.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{RL Algorithms for Mini-Games} $|$ \emph{Python, RL}}{}
    \resumeItemListStart
      \resumeItem{Implemented and analyzed MCTS, REINFORCE with baseline, and actor-critic algorithms across multiple environments including Grid World, Acrobot, Cat vs Monsters, and Cliff Walking.}
      \resumeItem{Optimized decision-making strategies and policy learning in stochastic domains, comparing convergence speed and sample efficiency.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Advanced Robot Navigation and Localization} $|$ \emph{Python, Robotics}}{}
    \resumeItemListStart
      \resumeItem{Developed a particle filter algorithm for robot localization achieving 0.5m position accuracy.}
      \resumeItem{Implemented and compared Q-learning and SARSA algorithms for autonomous robot wall-following with 100\% success rate in complex scenarios.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Ambulatory System (Hospital Recommender System)} $|$ \emph{Java, Android Studio, Python, ML, Selenium}}{}
    \resumeItemListStart
      \resumeItem{Built an Android application in Java that computed a patient Critical Index (CI) using linear regression on vital parameters (age, heart rate, temperature, SBP, DBP, SpO2) to support urgency-aware hospital recommendations.}
      \resumeItem{Developed a content-based recommender using cosine similarity to rank hospitals within a 5 km radius; automated dataset creation via Google Maps API and Python Selenium web scraping.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Bus Management System} $|$ \emph{Java, Android Studio, PHP, MySQL}}{}
    \resumeItemListStart
      \resumeItem{Developed a web and Android-based bus ticketing and route management system with separate user and admin interfaces for booking, route management, and transport operations.}
      \resumeItem{Implemented the backend using PHP and MySQL, and the Android client in Java, applying DBMS concepts for structured data storage and CRUD-based workflow management.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Data Conversion to YouTube Video for Unlimited Storage} $|$ \emph{Python, YouTube Data API}}{}
    \resumeItemListStart
      \resumeItem{Developed a web application that encodes arbitrary binary data into video frames and uploads it to YouTube via the YouTube Data API, enabling an unconventional approach to scalable cloud storage.}
      \resumeItem{Designed a full pipeline covering binary-to-pixel encoding, video generation, API-authenticated upload, and retrieval decoding, demonstrating end-to-end systems thinking.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Adaptive Personalized Travel Information Simulation} $|$ \emph{Python, Probabilistic Inference}}{}
    \resumeItemListStart
      \resumeItem{Developed a simulation system for real-time analysis of traveler choices and adaptation behavior, using the Metropolis-Hastings algorithm and efficient approximations to reduce computation time from 382s to 1.79s over an existing Gibbs sampling approach.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Query Bar for Music Info} $|$ \emph{Python, SPARQL, MusicBrainz}}{}
    \resumeItemListStart
      \resumeItem{Built a music information retrieval system using SPARQL and Python to query the MusicBrainz knowledge base for artist-song relationships.}
      \resumeItem{Applied knowledge modeling and semantic web concepts to enable structured querying over linked music data.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------HONORS & AWARDS-----------
\section{Honors \& Awards}
\resumeSubHeadingListStart
  \resumeItem{\textbf{IIT Kharagpur -- JEE Advanced} (2017): Admitted through one of India's most competitive engineering examinations, with acceptance among the top 0.1\% of over 1.2 million applicants nationwide.}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
